### 2024-02-21 documentation/thesis/thesis_document.tex
.

\[\frac{1000}{1000000} \times 50 \, mT = 0.05 \, mT \]

@@

\[ 0.05 \, mT \times 1000 = 50 \, \mu T \]

@@

A Hall effect sensor utilises the Hall effect that occurs when current
flows in a conductor through which a magnetic field passes. The sensor
consists of a semiconductor material such as gallium arsenide or indium
antimonide. Inside the sensor are Hall effect plates, which essentially
consist of a thin layer of this semiconductor material \customcite{BJJ16}.

@@

\begin{longtable}[]{@{}lllll@{}}
\caption{List of in unified firmware implemented digital magnetic field
sensors with focus on different sensor capabilities
\label{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}}\tabularnewline
\toprule
& TLV493D-A1B6 & HMC5883L & MMC5603NJ & AS5510\tabularnewline
\midrule
\endfirsthead
\toprule
& TLV493D-A1B6 & HMC5883L & MMC5603NJ & AS5510\tabularnewline
\midrule
\endhead
Readout-Axis & 3D & 3D & 3D & 1D\tabularnewline
Temperature-Sensor & yes & no & yes & no\tabularnewline
Resolution {[}uT{]} & 98 & 0.2 & 0.007 & 48\tabularnewline
Range {[}mT{]} & ±130.0 & ±0.8 & ±3 & ±50\tabularnewline
Interface & \gls{i2c} & \gls{i2c} & \gls{i2c} & \gls{i2c}\tabularnewline
\bottomrule
\end{longtable}

@@

One problem with the use of several sensors on one readout host \gls{pc}
is that the measurements may drift over time. On the one hand, \gls{usb}
latencies can occur. This can occur due to numerous factors, including
device drivers, data transfer speed and system resources. High-quality
\gls{usb} devices and modern drivers often minimise
latencies.\customcite{WSB19} Nevertheless, complex data processing tasks
and overloaded \gls{usb} ports can lead to delays.

@@

\begin{itemize}
\tightlist
\item
  \emph{std\_deviation} - \gls{sd}
\item
  \emph{mean} - Mean value
\item
  \emph{variance} - Variance
\item
  \emph{CoG} - Centre of gravity
\item
  \emph{binning} - Distribution of a sample by means of a histogram
\item
  \emph{k-nearest} - K-nearest neighbours
\end{itemize}

@@

The \emph{MRPProxy} module in figure
\ref{MRP_library_proxy_module_usage_example_with_host_(+pc)_for_readout_processing_and_remote_(+pc)_for_sensor_communication_using_the_http_protocol.png}
has been developed to allow forwarding and interaction with several
sensors over a network connection using a \gls{rest} interface.

The approach of implementing this via a \gls{rest} interface also offers
the advantage that several measurements or experiments can be recorded
at the same time with one remote sensor setup.

@@

Immediately after starting the \emph{MRPProxy}, the \gls{uuid}s of all
locally connected sensors are read out. These are stored together with
the class instance of the \emph{MRPHal} module in a \gls{lut}. This
makes it possible to address and interact with a sensor directly using
its \gls{uuid}. When using sensors with the same capabilities, these
must be combined. These are used to select the appropriate measurement
mode for a measurement. For this purpose, the \emph{info} command of
each sensor is queried. This information is added to the previously
created \gls{lut}. Duplicate entries are summarised (see table
\ref{Sensor_capabilities_merging_algorithm.csv}) and returned to the
host when the \emph{info} \ref{lst:mtsc} command is received over
network.

@@

After generating simple measurements with random values in the previous
example in chapter \ref{mrpreading}, the next step is to record real
sensor data. For this purpose, the \emph{MRPHal} module is developed,
which can interact with all \emph{Unified Sensor} from chapter
\ref{unified-sensor}-compatible sensors. In the following example
listing \ref{lst:mrpexample_hal}, an \emph{1D: Single Sensor}, which is
explained in chapter \ref{d-single-sensor}, is connected locally to the
host \gls{pc}.

@@

If no hardware sensor is available for the generation of test data, the
\emph{MRPSimulation} module is available. This contains a series of
functions that simulate various magnets and their fields. The result is
a complete \emph{MRPReading} measurement with a wide range of set meta
data.

The example listing \ref{lst:mrpexample_simulation} illustrates the
basic usage. Different variations of the \emph{generate\_reading}
function offer the user additional parameterisation options, such as
random polarisation direction or a defined centre-of-gravity vector. The
data is generated in the background using the \emph{magpylib}
\customcite{OB20} library according to the specified parameters.

@@

The parameter \_readings should later receive the imported measurements
from the \emph{stage rawimport} in listing
\ref{lst:pipeline_mrp_evaluation_yaml} and the optional
\emph{IP\_return\_count} parameter specifies the number of best
measurements that are returned. The return parameter is a list of
measurements containing the most similar measurements, measured by the
smallest distance between all measurements. The distance for each
measurement is determined using the centre of gravity function
\emph{CoG}, the length is then calculated from the result vector. This
value can then be used for sorting.

\begin{lstlisting}[language=Python, caption={User implemented custom find most similar readings algorithm}, label=lst:custom_find_similar_values_algorithm]
@staticmethod
def FindSimilarValuesAlgorithm(_readings: [MRPReading.MRPReading], IP_return_count: int = -1) -> [MRPReading.MRPReading]:
  import heapq
  import math
  heap = []
  # SET RESULT VALUE COUNT
  IP_return_count = max([int(IP_return_count),len(_readings)])
  if IP_return_count < 0:
      IP_return_count = len(_readings) / 5
  # CALCULATE TARGET VALUE: CENTER OF GRAVITY MAGNITUDE FOR ALL READINGS
  target_value = 0.0
  for idx, r in enumerate(_readings):
      cog = MRPAnalysis.MRPAnalysis.calculate_center_of_gravity(r)
      # COMPUTE LENGTH OF VECTOR
      cog_value: float = math.sqrt(cog[0]**2 + cog[1]**2 cog[2]**2)
      target_value = target_value + cog
  target_value = target_value / len(_readings)
  # PUSH READINGS TO HEAP
  for value in _readings:
      # USE DIFF AS PRIORITY VALUE IN MIN-HEAP
      cog = MRPAnalysis.MRPAnalysis.calculate_center_of_gravity(value)
      cog_value: float = math.sqrt(cog[0]**2 + cog[1]**2 cog[2]**2)
      diff = abs(cog_value - target_value)
      heapq.heappush(heap, (diff, cog_value))
  # RETURN X BEST ITEMS FROM HEAP
  similar_values = [item[1] for item in heapq.nsmallest(IP_return_count, heap)]
  # CLEAN UP USED LIBRARIES AND RETURN RESULT
  del heapq
  del math
  return similar_values
\end{lstlisting}

The calculated distances from the \emph{CoG} value of the measurements
to are inserted into a \emph{heapq} priority queue. As the measured
values are full sphere measurements, the \emph{CoG} in this
implementation is calculated using this formula:

\[\text{CoG} = \frac{\sum{D_{istance} \times W_{eight}}}{\sum{W_{eight}}}\]

@@

Subsequently, as many elements of the queue are returned as defined by
the \emph{IP\_return\_count} parameter. The actual sorting is carried
out by the queue in the background.

@@

\begin{lstlisting}[caption={User defined processing pipeline using custom implemented filter algorithm in third stage}, label=lst:pipeline_mrp_evaluation_yaml]
settings:
  enabled: true
  export_intermediate_results: false
  name: pipeline_mrp_evaluation

stage rawimport:
  function: import_readings
  parameters:
    IP_input_folder: ./readings/evaluation/
    IP_file_regex: 360_(.)*.mag.json

@@

Also, the figure
\ref{MRP_evaluation_result_after_find_similar_values_algorithm_execution_in_the_user_defined_pipeline.png}
illustrates, the measured values are plotted as a result of the filter
algorithm. As the \emph{IP\_return\_count} parameter is set to four,
only the four most similar measurements are exported. It can be seen
from the plotted \emph{CoG} \(\mu\)T deviation values, that these are
closest to an ideal Magnet with a CoG value of 0\(\mu\)T. This ideal
value is calculated with the function
\emph{MRP.MRPSimulation.generate\_simulated\_reading}, with the same
measurement parameters (magnet type, dimensions, sensor distance) as
they correspond to the mechanical structure of the used hardware sensor
in chapter \ref{d-full-sphere}.

@@

It is possible to carry out the sensor characterisation demonstrated for
other compatible sensors using the same procedure. Pre-configured
measurements in chapter \ref{command-line-interface} and analysis
pipelines in chapter \ref{programmable-data-processing-pipeline}, which
are available for this purpose, are packaged within the library.

The following parameters are determined and analysed for the sensor
evaulation:

@@

The sensor platform used is an adapted version of the \emph{1D: Single
Sensor} from chapter \ref{d-single-sensor} sensor platform. The sensors
to be measured are fixed together on an aluminium plate with thermally
conductive adhesive. This compensates for thermal differences. This is
essential for the subsequent temperature deviation tests in order to
obtain comparable measurement results.\customcite{J21}

@@

The following figure
\ref{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}
contains the measured values of these sensors. In the next phases these
are analysed for each sensor examined.

The following data is shown in the plots:

@@

The temperature stability of the \emph{TLV493D} with a mean value of
20.68\(^{\circ}\)C and a \gls{sd} of
\(\sigma_{t,tlv}\)=0.53\(^{\circ}\)C indicates a consistent trend. This
implies a constant tendency. The close grouping of the measured values
around the mean value indicates good stability. The confidence interval
is expected to be between \emph{20.15\(^{\circ}\)C} and
\emph{21.21\(^{\circ}\)C}, which indicates a stable and consistent
temperature measurement. This result is noisier compared to the
temperature stability of the \emph{MMC5603} with stable
\emph{19.40\(^{\circ}\)C} with an accuracy of two decimal places.

@@

The noise of the sensor is drawn around this using the blue line. For
the \emph{TLV493D} the \gls{sd}
\emph{\(\sigma_{rv,tlv}\)=172.0\({\mu}\)T}, which is twice the value
given by the datasheet as the noise value (refer to table
\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}).
Under the same conditions, the \emph{MMC5603NJ} undercuts the value
specified by the manufacturer. The \gls{sd} approaches
\emph{\(\sigma_{rv, mmc}\)=0.20\({\mu}\)T} and is negligible, especially
when additional averaging is used.

@@

The sensor linearity of a magnetic field sensor or describes the ability
of the sensor to provide a proportional linear response to changes in
the magnetic field without non-linear distortions \customcite{CSG22}. This
means that the output signals of the sensor vary directly proportional
to the input magnetic fields without deviations or distortions and is
therefore an important indicator for measurements of fields at different
distances or objects.

This is achieved by means of an additional linear axis installed above
the sensor setup. A holder for an \emph{N45 12x12x12mm} magnet is
attached to the end effector of this axis, which can thus be moved at
different distances above the respective sensor \gls{ic}. The ambient
temperature is set to \emph{\(\mu_{trev, 7055BT}\)=21.0\(^{\circ}\)C} in
the measurement runs and thus corresponds to the same conditions as in
the \emph{Background Noise} chapter
\ref{sensor-characterisation-background-noise} setup.

@@

As the temperature sensor \emph{TLV493D} in particular produced vastly
different results in the previous measurements, an additional
temperature sensor is attached to the sensor circuit board for this
measurement. The figure
\ref{Sensor_evaluation_setup_for_temperature_sensitivity_measurements.png}
represents these modifications in detail. These changes makes it
possible to accurately determine the sensors \gls{ic} temperature. The
temperature measuring device \emph{7055BT} can be analysed using a
\gls{pc} interface. The controller of the temperature chamber can also
be programmed via a \gls{pc} interface and a target temperature can be
specified.

@@

\begin{longtable}[]{@{}lllll@{}}
\caption{Overview of all characterised sensor properties
\label{Overview_of_all_characterised_sensor_properties.csv}}\tabularnewline
\toprule
Symbol & TLV493D & MMC5603NJ & Unit & Description\tabularnewline
\midrule
\endfirsthead
\toprule
Symbol & TLV493D & MMC5603NJ & Unit & Description\tabularnewline
\midrule
\endhead
\(N_{baseline}\) & 10000 & 10000 & - & Number of samples measured for
baseline run\tabularnewline
\(N_{measurement}\) & 2000 & 2000 & - & Number of samples measured for
measurement run\tabularnewline
\(\mu_{nl}\) & 0.79 & 0.00 & \% & Mean noise level\tabularnewline
\(\sigma_{nl}\) & 0.76 & 0.00 & \% & \gls{sd} noise level\tabularnewline
\(\mu_{rv}\) & 157.23 & -50.39 & \(\mu\)T & Mean Baseline without offset
compensation\tabularnewline
\(\sigma_{rv}\) & 172.00 & 0.20 & \(\mu\)T & \gls{sd} sensor
value\tabularnewline
\(\mu_{t}\) & 20.68 & 19.40 & \(^{\circ}\)C & Mean sensor
temperature\tabularnewline
\(\sigma_{t}\) & 0.53 & 0.00 & \(^{\circ}\)C & \gls{sd} sensor
temperature\tabularnewline
\(\mu_{trev}\) & 21.0 & 21.0 & \(^{\circ}\)C & Ambient
temperature\tabularnewline
\(\mu_{sl}\) & 0.25 & 0.04 & \% & Mean sensor linearity
deviation\tabularnewline
\(\sigma_{sl}\) & 3.64 & 0.56 & \% & \gls{sd} sensor
linearity\tabularnewline
\(\mu_{td}\) & -1.99 & -5.13 & \(\mu\)T / \(^{\circ}\)C & Mean sensor
temperature coefficients\tabularnewline
DR & {[}-138;220{]} & {[}-3.1;3.4{]} & \(\mu\)T & maximum linear
\gls{dr}\tabularnewline
\bottomrule
\end{longtable}

@@

The \emph{MMC5603NJ} can be used directly without additional software
calibration for measuring permanent magnets. Even without additional
measurement averaging, very precise measurement results can be achieved,
which achieve a measurement accuracy of less than \emph{1000 \gls{ppm}}.

However, due to the limited \gls{dr} of around \emph{±3mT}, direct
measurement of stronger magnets is not possible using the
\emph{MMC5603NJ}. The \emph{N45 12x12x12mm} magnets used in the
application typically have a field strength of around \emph{100mT} at a
distance of \emph{10mm} which is more than the \emph{MMC5603NJ} can
measure.

The \emph{TLV493D}, on the other hand, is able to measure these ranges
with a specified \gls{dr} of \emph{±150mT}, but does not achieve the
required accuracy due to strong noise and steep temperature
coefficients. In the following chapter, recommendations for action are
defined, which are derived from the analysis results.

>>>>

\noteworthy{\frac{1000}{1000000} \times 50 \, mT = 0.05 \, mT }{1000ppm from 50mT needed resolution calucation I}

@@

\noteworthy{0.05 \, mT \times 1000 = 50 \, \mu T}{1000ppm from 50mT needed resolution calucation II}

@@

A Hall effect sensor utilises the Hall effect that occurs when current
flows in a conductor that is exposed to a magnetic field. The sensor
consists of a semiconductor material such as gallium arsenide or indium
antimonide. Inside the sensor are Hall effect plates, which essentially
consist of a thin layer of this semiconductor material. \customcite{BJJ16}

The figure
\ref{Typical_block_diagram_of_a_digital_hall_sensor_sensing_chain_using_three_hall_plates.png}
shows the internal structure of a digital Hall effect sensor as a block
diagram. The Hall effect takes place in the Hall plates. These are
orientated differently depending on the axis inside the \gls{ic}s. In
this case, it is a three-axis hall effect sensor. The output voltage
generated by the Hall plates is then digitised by a \gls{adc}. The
values can then be read out via a digital interface.

@@

\begin{longtable}[]{@{}lllll@{}}
\caption{List of in unified firmware implemented digital magnetic field
sensors with focus on different sensor capabilities
\label{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}}\tabularnewline
\toprule
& TLV493D & HMC5883L & MMC5603NJ & AS5510\tabularnewline
\midrule
\endfirsthead
\toprule
& TLV493D & HMC5883L & MMC5603NJ & AS5510\tabularnewline
\midrule
\endhead
Readout-Axis & 3D & 3D & 3D & 1D\tabularnewline
Temperature-Sensor & yes & no & yes & no\tabularnewline
Resolution {[}uT{]} & 98 & 0.2 & 0.007 & 48\tabularnewline
Range {[}mT{]} & ±130.0 & ±0.8 & ±3 & ±50\tabularnewline
Interface & \gls{i2c} & \gls{i2c} & \gls{i2c} & \gls{i2c}\tabularnewline
\bottomrule
\end{longtable}

@@

One problem with the use of several sensors on one readout host \gls{pc}
is that the measurements may drift over time. On the one hand, \gls{usb}
latencies can occur. This can occur due to numerous factors, including
device drivers, data transfer speed and system resources. High-quality
\gls{usb} devices and modern drivers often minimise latencies.
\customcite{WSB19} Nevertheless, complex data processing tasks and
overloaded \gls{usb} ports can lead to delays.

@@

\begin{itemize}
\tightlist
\item
  \emph{std\_deviation} - \gls{sd}
\item
  \emph{mean} - Mean value
\item
  \emph{variance} - Variance
\item
  \emph{binning} - Distribution of a sample by means of a histogram
  using bins
\item
  \emph{k-nearest} - K-nearest neighbours
\end{itemize}

@@

The \emph{MRPProxy} module in figure
\ref{MRP_library_proxy_module_usage_example_with_host_(+pc)_for_readout_processing_and_remote_(+pc)_for_sensor_communication_using_the_http_protocol.png}
has been developed to allow forwarding and interaction with several
sensors over a network connection using a \gls{rest} interface. The
approach of implementing this via a \gls{rest} interface also offers the
advantage that several measurements or experiments can be recorded at
the same time with one remote sensor setup.

@@

Immediately after starting the \emph{MRPProxy}, the \gls{uuid}s of all
locally connected sensors are read out. These are stored together with
the class instance of the \emph{MRPHal} module in a \gls{lut}. This
makes it possible to address and interact with a sensor directly using
its \gls{uuid}. When using sensors with the same capabilities, these
must be combined. These are used to select the appropriate measurement
mode for a measurement. For this purpose, the \emph{info} command of
each sensor is queried. This information is added to the previously
created \gls{lut}. Duplicate entries are summarised (see table
\ref{Sensor_capabilities_merging_algorithm.csv}) and returned to the
host when the \emph{info} \ref{lst:mtsc} command is received over
network. \newpage

@@

After generating simple measurements with random values in the previous
example in chapter \ref{mrpreading}, the next step is to record real
sensor data. For this purpose, the \emph{MRPHal} module is developed,
which can interact with all \emph{Unified Sensor} from chapter
\ref{unified-sensor}-compatible sensors. In the following example
listing \ref{lst:mrpexample_hal}, an \emph{1D: Single Sensor}, which is
explained in chapter \ref{d-single-sensor}, is connected locally to the
host \gls{pc}. \newpage

@@

If no hardware sensor is available for the generation of test data, the
\emph{MRPSimulation} module is available. This contains a series of
functions that simulate various magnets and their fields. The result is
a complete \emph{MRPReading} measurement with a wide range of set meta
data. The example listing \ref{lst:mrpexample_simulation} illustrates
the basic usage. Different variations of the \emph{generate\_reading}
function offer the user additional parameterisation options, such as
random polarisation direction or a defined centre-of-gravity vector. The
data is generated in the background using the \emph{magpylib}
\customcite{OB20} library according to the specified parameters.

@@

The parameter \_readings should later receive the imported measurements
from the \emph{stage rawimport} in listing
\ref{lst:pipeline_mrp_evaluation_yaml} and the optional
\emph{IP\_return\_count} parameter specifies the number of best
measurements that are returned. The return parameter is a list of
measurements containing the most similar measurements, measured by the
smallest distance between all measurements.

The sorting indicator for each measurement is determined using the
\emph{\gls{cog}} function and is implemented using the following
equation:

\noteworthy{\text{CoG} = \frac{\sum{D_{istance} \times W_{eight}}}{\sum{W_{eight}}}}{Center of Gravity}

@@

\begin{lstlisting}[language=Python, caption={User implemented custom find most similar readings algorithm}, label=lst:custom_find_similar_values_algorithm]
@staticmethod
def FindSimilarValuesAlgorithm(_readings: [MRPReading.MRPReading], IP_return_count: int = -1) -> [MRPReading.MRPReading]:
  import heapq
  import math
  heap = []
  # SET RESULT VALUE COUNT
  IP_return_count = max([int(IP_return_count),len(_readings)])
  if IP_return_count < 0:
      IP_return_count = len(_readings) / 5
  # CALCULATE TARGET VALUE: CENTER OF GRAVITY MAGNITUDE FOR ALL READINGS
  target_value = 0.0
  for idx, r in enumerate(_readings):
      cog = MRPAnalysis.MRPAnalysis.calculate_center_of_gravity(r)
      # COMPUTE LENGTH OF VECTOR = B value
      cog_value: float = math.sqrt(cog[0]**2 + cog[1]**2 cog[2]**2)
      target_value = target_value + cog
  target_value = target_value / len(_readings)
  # PUSH READINGS TO HEAP
  for value in _readings:
      # USE DIFF AS PRIORITY VALUE IN MIN-HEAP
      cog = MRPAnalysis.MRPAnalysis.calculate_center_of_gravity(value)
      cog_value: float = math.sqrt(cog[0]**2 + cog[1]**2 cog[2]**2)
      diff = abs(cog_value - target_value)
      heapq.heappush(heap, (diff, cog_value))
  # RETURN X BEST ITEMS FROM HEAP
  similar_values = [item[1] for item in heapq.nsmallest(IP_return_count, heap)]
  # CLEAN UP USED LIBRARIES AND RETURN RESULT
  del heapq
  del math
  return similar_values
\end{lstlisting}

The calculated distances from the \emph{\gls{cog}} value of the
measurements to are inserted into a \emph{heapq} priority queue.
Subsequently, as many elements of the queue are returned as defined by
the \emph{IP\_return\_count} parameter. The actual sorting is carried
out by the queue in the background.

@@

\begin{lstlisting}[caption={User defined processing pipeline using custom implemented filter algorithm in third stage}, label=lst:pipeline_mrp_evaluation_yaml]
name: pipeline_mrp_evaluation
stage rawimport:
  function: import_readings
  parameters:
    IP_input_folder: ./readings/evaluation/
    IP_file_regex: 360_(.)*.mag.json

@@

Also, the figure
\ref{MRP_evaluation_result_after_find_similar_values_algorithm_execution_in_the_user_defined_pipeline.png}
illustrates, the measured values are plotted as a result of the filter
algorithm. As the \emph{IP\_return\_count} parameter is set to four,
only the four most similar measurements are exported. It can be seen
from the plotted \emph{\gls{cog}} \(\mu\)T deviation values, that these
are closest to an ideal Magnet with a CoG value of 0\(\mu\)T. This ideal
value is calculated with the function
\emph{MRP.MRPSimulation.generate\_simulated\_reading}, with the same
measurement parameters (magnet type, dimensions, sensor distance) as
they correspond to the mechanical structure of the used hardware sensor
in chapter \ref{d-full-sphere}.

@@

It is possible to carry out the sensor characterisation demonstrated for
other compatible sensors using the same procedure. Pre-configured
measurements in chapter \ref{command-line-interface} and analysis
pipelines in chapter \ref{programmable-data-processing-pipeline}, which
are available for this purpose, are packaged within the library. The
following parameters are determined and analysed for the sensor
evaulation:

@@

The sensor platform used is an adapted version of the \emph{1D: Single
Sensor} from chapter \ref{d-single-sensor} sensor platform. The sensors
to be measured are fixed together on an aluminium plate with thermally
conductive adhesive. This compensates for thermal differences. This is
essential for the subsequent temperature deviation tests in order to
obtain comparable measurement results. \customcite{J21}

@@

The following figure
\ref{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}
contains the measured values of these sensors. In the next phases these
are analysed for each sensor examined. The following data is shown in
the plots:

@@

The temperature stability of the \emph{TLV493D} with a mean value of
20.68\(^{\circ}\)C and a \gls{sd} of
\(\sigma_{t,TLV493D}\)=0.53\(^{\circ}\)C indicates a consistent trend.
This implies a constant tendency. The close grouping of the measured
values around the mean value indicates good stability. The confidence
interval is expected to be between \emph{20.15\(^{\circ}\)C} and
\emph{21.21\(^{\circ}\)C}, which indicates a stable and consistent
temperature measurement. This result is noisier compared to the
temperature stability of the \emph{MMC5603} with stable
\emph{\(\mu_{t, MMC5603NJ}\)=0.53\(^{\circ}\)C} with an accuracy of two
decimal places.

@@

The noise of the sensor is drawn around this using the blue line. For
the \emph{TLV493D} the \gls{sd}
\emph{\(\sigma_{rv,TLV493D}\)=172.0\({\mu}\)T}, which is twice the value
given by the datasheet as the noise value (refer to table
\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}).
Under the same conditions, the \emph{MMC5603NJ} undercuts the value
specified by the manufacturer. The \gls{sd} approaches
\emph{\(\sigma_{rv, MMC5603NJ}\)=0.20\({\mu}\)T} and is negligible,
especially when additional averaging is used.

@@

The sensor linearity of a magnetic field sensor or describes the ability
of the sensor to provide a proportional linear response to changes in
the magnetic field without non-linear distortions \customcite{CSG22}. This
means that the output signals of the sensor vary directly proportional
to the input magnetic fields without deviations or distortions and is
therefore an important indicator for measurements of fields at different
distances or objects. This is achieved by means of an additional linear
axis installed above the sensor setup. A holder for an \emph{N45
12x12x12mm} magnet is attached to the end effector of this axis, which
can thus be moved at different distances above the respective sensor
\gls{ic}. The ambient temperature is set to
\emph{\(\mu_{trev, 7055BT}\)=21.0\(^{\circ}\)C} in the measurement runs
and thus corresponds to the same conditions as in the \emph{Background
Noise} chapter \ref{sensor-characterisation-background-noise} setup.

@@

As the temperature sensor \emph{TLV493D} in particular produced vastly
different results in the previous measurements, an additional
temperature sensor is attached to the sensor circuit board for this
measurement.

The figure
\ref{Sensor_evaluation_setup_for_temperature_sensitivity_measurements.png}
represents these modifications in detail. These changes makes it
possible to accurately determine the sensors \gls{ic} temperature. The
temperature measuring device \emph{7055BT} can be analysed using a
\gls{pc} interface. The controller of the temperature chamber can also
be programmed via a \gls{pc} interface and a target temperature can be
specified.

@@

\begin{longtable}[]{@{}lllll@{}}
\caption{Overview of all characterised sensor properties
\label{Overview_of_all_characterised_sensor_properties.csv}}\tabularnewline
\toprule
Symbol & TLV493D & MMC5603NJ & Unit & Description\tabularnewline
\midrule
\endfirsthead
\toprule
Symbol & TLV493D & MMC5603NJ & Unit & Description\tabularnewline
\midrule
\endhead
\(N_{baseline}\) & 10000 & 10000 & - & Samples measured for
baseline\tabularnewline
\(N_{measurement}\) & 2000 & 2000 & - & Samples measured for
measurement\tabularnewline
\(\mu_{nl}\) & 0.79 & 0.00 & \% & Mean noise level\tabularnewline
\(\sigma_{nl}\) & 0.76 & 0.00 & \% & \gls{sd} noise level\tabularnewline
\(\mu_{rv}\) & 157.23 & -50.39 & \(\mu\)T & Baseline without offset
compensation\tabularnewline
\(\sigma_{rv}\) & 172.00 & 0.20 & \(\mu\)T & \gls{sd} sensor
value\tabularnewline
\(\mu_{t}\) & 20.68 & 19.40 & \(^{\circ}\)C & Mean sensor
temperature\tabularnewline
\(\sigma_{t}\) & 0.53 & 0.00 & \(^{\circ}\)C & \gls{sd} sensor
temperature\tabularnewline
\(\mu_{trev}\) & 21.0 & 21.0 & \(^{\circ}\)C & Ambient
temperature\tabularnewline
\(\mu_{sl}\) & 0.25 & 0.04 & \% & Mean sensor linearity
deviation\tabularnewline
\(\sigma_{sl}\) & 3.64 & 0.56 & \% & \gls{sd} sensor
linearity\tabularnewline
\(\mu_{td}\) & -1.99 & -5.13 & \(\mu\)T / \(^{\circ}\)C & Sensor
temperature coefficients\tabularnewline
DR & {[}-138;220{]} & {[}-3.1;3.4{]} & \(\mu\)T & maximum linear
\gls{dr}\tabularnewline
\bottomrule
\end{longtable}

@@

The \emph{MMC5603NJ} can be used directly without additional software
calibration for measuring permanent magnets. Even without additional
measurement averaging, very precise measurement results can be achieved,
which achieve a measurement accuracy of less than \emph{1000 \gls{ppm}}.
Due to the limited \gls{dr} of around \emph{±3mT}, direct measurement of
stronger magnets is not possible using the \emph{MMC5603NJ}. The
\emph{N45 12x12x12mm} magnets used in the application typically have a
field strength of around \emph{100mT} at a distance of \emph{10mm} which
is more than the \emph{MMC5603NJ} can measure. The \emph{TLV493D}, on
the other hand, is able to measure these ranges with a specified
\gls{dr} of \emph{±150mT}, but does not achieve the required accuracy
due to strong noise and steep temperature coefficients. In the following
chapter, recommendations for action are defined, which are derived from
the analysis results.
